---
title: "Fitting Weibull Distribution to FIA Data"
author: "Wesley Rancher"
date: "2025-04-29"
output: html_document
editor_options: 
  chunk_output_type: console
---

## From Sam Flake's code:

#This script has several steps:

# 1) import and wrangle FIA data for plots, trees, seedlings, and sitetrees
# 2) assemble FIA plots into age/species cohorts like LANDIS-II
# 3) estimate leaf area for plots using the same algorithm as NECN
# 4) get amount of regeneration per plot per species
# 5) fit distributions to regen~LAI values, with a few options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#libraries
library("tidyverse")
library("rFIA")
library("nls2")
library("minpack.lm")
library("sf")
```

## Weibull Function

```{r}
#function to fit the weibull distribution curve to binned data using NLS
fit_weibull <- function(dat, lower = c(-Inf, -Inf, 0, 0), upper = c(Inf, Inf, Inf, 10), use_c_d = "both") {
  
  #you might have to play with these starting values
  pars <- expand.grid(a=seq(0.1,10, len=50), #shape
                      b=seq(0.1, 20, len=10), #scale
                      c = 0, #threshold parameter; this sets the "floor" for the curve,
                      # the y-intercept for shape parameter > 1
                      # or asymptote for low values of shape parameters
                      d=seq(0.1, 20, len = 20) #removed d parameter, which scales everything vertically
                      #it does allow better fit but harder to converge
  )
  
  
  # a floor could be set by replacing c with a constant, rather than 
  # estimating it, though this could cause issues with convergence.
  # first round to get approximate starting values
  if(use_c_d == "both") formula <- prop_present ~ (((a/b) * ((lai/b)^(a-1)) * exp(- (lai/b)^a)) + c) * d
  if(use_c_d == "c"){
    formula <- prop_present ~ (((a/b) * ((lai/b)^(a-1)) * exp(- (lai/b)^a)) + c)
    pars <- pars[,c(1:3)]
    lower = lower[c(1:3)]
    upper = upper[c(1:3)]
  } 
  if(use_c_d == "d") {
    formula <- prop_present ~ (((a/b) * ((lai/b)^(a-1)) * exp(- (lai/b)^a))) * d
    pars <- pars[,c(1,2,4)]
    lower = lower[c(1,2,4)]
    upper = upper[c(1,2,4)]
  }
  if(use_c_d == "neither"){
    formula <- prop_present ~ (((a/b) * ((lai/b)^(a-1)) * exp(- (lai/b)^a)))
    pars <- pars[,c(1,2)]
    lower = lower[c(1,2)]
    upper = upper[c(1,2)]
  }
  
  res <- nls2(formula, 
              data=dat,
              start=pars, 
              algorithm='brute-force',
              upper = upper,
              lower = lower,
              weights = dat$n_plots_bin)
  
  #get better estimates using minpack
  res1 <- nlsLM(formula, 
                data=dat,
                start=as.list(coef(res)),
                upper = upper,
                lower = lower,
                weights = dat$n_plots_bin)
  
  #sometimes c will be negative, which would allow seedlings to sometimes be negative.
  #If that happens, refit the model with c = 0
  if(use_c_d %in% c("both", "c") & coef(res1)[3] < 0) {
    res1 <- nlsLM(prop_present ~ ((a/b) * ((lai/b)^(a-1)) * exp(- (lai/b)^a)),
                  data=dat,
                  start=as.list(coef(res)[c(1,2)]))
  }
  
  
  return(res1)
}
```

## Predefined parms to call later 
## These determine how the FIA data is filtered and metrics to consider for the Weibull function

```{r}
options(scipen = 999)
#should we restrict our analysis to plots that are near seedlings, near adult trees, or unrestricted?
#this is by far the slowest part of the script
range_method <- "seedling" #"seedling" or "adult"; other options skip this step and use all the data from the chosen states
#range buffer size -- how many meters can plots be from seedlings to count in the calculation?
range_buffer <- 10000
#should maximum suitability be set to 1 and everything scaled to match? This will (almost?)
# always increase total suitable light levels and thus regeneration
scale_max_p <- TRUE
#should the area under the curve be set to 1 for all species? This will cancel out
# differences in abundance/fecundity among species. Probably not recommended if you hae
# a lot of range-restricted species, unless you're using the range_method option above.
# But this is very much recommended if you're wanting to fit a true Weibull PDF where AUC = 1 
# (i.e. using use_c_d == "neither")
set_auc_to_1 <- FALSE
#what formula should we use? See above equation fit_weibull. For a regular Weibull PDF,
# set use_c_d = "neither", to only use the shape and scale parameters. Otherwise,
# you can use the c parameter to translate the whole curve up or the d parameter to stretch the
# whole curve. This gives more flexibility in the kinds of shapes that can be fit,
# and allows for the area under the curve to be greater than 1.
use_c_d <- "d"
```

## Wranging FIA data

```{r}
#using rFIA table
tables <- c("TREE","SEEDLING","PLOT", "COND", "SITETREE")
#directory <- "D:/Data/fia/rFIA_downloads"
directory <- "F:/SoutheastAlaska/landis/scripts/LAI establishment from FIA data/example_data/"

#species reference data
sp_ref <- read.csv(paste0(directory, "REF_SPECIES.csv"))

#import fia data
#using rFIA package automatically knits the tables together; you could also
# use readr::read_csv() or import several csvs then rbind() 
fia <- getFIA(dir = "F:/SoutheastAlaska/data/",
               tables = tables,
               states = 'AK')

trees <- fia$TREE
plot <- fia$PLOT
cond <- fia$COND
seedlings <- fia$SEEDLING
sitetrees <- fia$SITETREE

rm(fia)
gc()
```

## Filtering by plot conditions

```{r}
# Filter what plots to use -----------------------------------------------------
# Not all plots are in forest, some have been recently treated, etc, and we need
# to filter those out

cond_to_use <- cond %>%
  filter(!(DSTRBCD1 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD2 %in% c(30,31,32,46,53,54,80)),
         !(DSTRBCD3 %in% c(30,31,32,46,53,54,80)),
         TRTCD1 == 0 | is.na(TRTCD1),
         TRTCD2 == 0 | is.na(TRTCD2),
         TRTCD3 == 0 | is.na(TRTCD3)) %>%
  mutate(IS_FOREST = ifelse(FORTYPCD %in%(c(1:998)), 1, 0)) %>%
  group_by(PLT_CN) %>%
  summarise(total_cond = sum(CONDPROP_UNADJ),
            natural = sum(STDORGCD, na.rm = TRUE),
            treatment = sum(TRTCD1, na.rm = TRUE),
            proportion_forest = sum(CONDPROP_UNADJ * IS_FOREST)) %>%
  filter(total_cond > 0.95,
         proportion_forest > 0.95)

plots_to_use <- plot %>%
  filter(PLOT_STATUS_CD == 1) %>%
  left_join(cond_to_use, by = c("CN" = "PLT_CN")) %>%
  dplyr::select(CN, proportion_forest)
```

## Crosswalk to LANDIS

```{r}
#southeast tables
simdir <- "F:/SoutheastAlaska/landis/simulations/North_Test/"
func_table <-  read.csv(paste0(simdir, "NECN_functional_parameters.csv"))
sp_table <- read.csv(paste0(simdir, "NECN_sp.csv")) #%>%
#  left_join(func_table, by = "FunctionalGroupIndex") 
unique(func_table$FunctionalGroupName)
unique(sp_table$SpeciesCode)
```

## Common join attribute is missing for Southeast so I manually assigned fuctional groups within the spp table and obtained species from the lookup table

```{r}
#interior AK (adding functionalgroupindex column)
sp_table <- read.csv(paste0(simdir, "NECN_sp.csv")) %>%
  mutate(FunctionalGroupIndex = case_when(
    SpeciesCode %in% c("SitkaSpruce", "WesternHemlock", "WesternRedcedar", "PacificSilverFir", "DouglasFir") ~ 1,
    SpeciesCode %in% "LodgepolePine" ~ 2,
    SpeciesCode %in% c("QuakingAspen", "BalsamPoplar", "PaperBirch") ~ 3,
    SpeciesCode %in% c("MountainHemlock", "AlaskaYellowCedar", "WhiteSpruce", 
                       "EngelmannSpruce", "SubalpineFir", "WesternWhitePine") ~ 4,
    SpeciesCode %in% "RedAlder" ~ 5,
    TRUE ~ NA_real_
  ))

#determine sp grp codes from FIA to grab
sp_ref$ScienceName <- paste0(sp_ref$GENUS, " ", sp_ref$SPECIES)#add column

grp1_names <- c("Picea sitchensis", "Tsuga heterophylla", "Thuja plicata", "Abies amabilis", "Pseudotsuga menziesii")
grp2_names <- "Pinus contorta"
grp3_names <- c("Populus tremuloides", "Populus balsamifera", "Betula papyrifera")
grp4_names <- c("Tsuga mertensiana", "Chamaecyparis nootkatensis", "Picea glauca", 
                "Picea engelmannii", "Abies lasiocarpa", "Pinus monticola")
grp5_names <- "Alnus rubra"

#filter the reference table to these species to get their codes
grp1_spcd <- sp_ref %>% filter(ScienceName %in% grp1_names) %>%
   distinct(ScienceName, SPCD)
grp2_spcd <- sp_ref %>% filter(ScienceName %in% grp2_names) %>%
   distinct(ScienceName, SPCD)
grp3_spcd <- sp_ref %>% filter(ScienceName %in% grp3_names) %>%
   distinct(ScienceName, SPCD)
grp4_spcd <- sp_ref %>% filter(ScienceName %in% grp4_names) %>%
   distinct(ScienceName, SPCD)
grp5_spcd <- sp_ref %>% filter(ScienceName %in% grp5_names) %>%
   distinct(ScienceName, SPCD)

lowElevCon <- c(grp1_spcd[[2]])
lodgepole <- grp2_spcd[[2]]
DecTrees <- c(grp3_spcd[[2]])
highElevCon <- c(grp4_spcd[[2]])
RedAlder <- grp5_spcd[[2]]

#grab functional group codes from FIA 
lowElevCon_grpcds <- unique(trees$SPGRPCD[trees$SPCD%in%lowElevCon])
lodgepole_grpcds <- unique(trees$SPGRPCD[trees$SPCD%in%lodgepole])
DecTrees_grpcds <- unique(trees$SPGRPCD[trees$SPCD%in%DecTrees])
highElevCon_grpcds <- unique(trees$SPGRPCD[trees$SPCD%in%highElevCon])
RedAlder_grpcds <- unique(trees$SPGRPCD[trees$SPCD%in%RedAlder])
```

## Assign each functional group KLAI and Max LAI

```{r}
#we need to assign each species group a value for KLAI and MaximumLAI
#this needs to be revised for new LANDIS projects
spgrp_lai <- data.frame(SPGRPCD = unique(trees$SPGRPCD),
                        FunctionalGroupIndex = numeric(length(unique(trees$SPGRPCD)))) %>%
  arrange(SPGRPCD) %>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% lowElevCon_grpcds, 1, FunctionalGroupIndex))%>% 
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% lodgepole_grpcds, 2, FunctionalGroupIndex))%>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% DecTrees_grpcds, 3, FunctionalGroupIndex)) %>% 
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% highElevCon_grpcds, 4, FunctionalGroupIndex)) %>%
  mutate(FunctionalGroupIndex = ifelse(SPGRPCD %in% RedAlder_grpcds, 5, FunctionalGroupIndex)) %>%
  left_join(sp_table %>% dplyr::select(FunctionalGroupIndex, KLAI, MaximumLAI))

sp_ref$SPECIES_SYMBOL[sp_ref$SPCD%in%lowElevCon]
sp_ref$SPECIES_SYMBOL[sp_ref$SPCD%in%lodgepole]
sp_ref$SPECIES_SYMBOL[sp_ref$SPCD%in%DecTrees]
sp_ref$SPECIES_SYMBOL[sp_ref$SPCD%in%highElevCon]
sp_ref$SPECIES_SYMBOL[sp_ref$SPCD%in%RedAlder]


sp_table <- sp_table %>%
  mutate(SpeciesCodeActual = case_when(
    SpeciesCode == "SitkaSpruce" ~ "PISI",
    SpeciesCode == "WesternHemlock" ~ "TSHE",
    SpeciesCode == "WesternRedcedar" ~ "THPL",
    SpeciesCode == "PacificSilverFir" ~ "ABAM",
    SpeciesCode == "DouglasFir" ~ "PSME",
    SpeciesCode == "LodgepolePine" ~ "PICO",
    SpeciesCode == "QuakingAspen" ~ "POTR5",
    SpeciesCode == "BalsamPoplar" ~ "POBA2",
    SpeciesCode == "PaperBirch" ~ "BEPA",
    SpeciesCode == "SubalpineFir" ~ "ABLAA",
    SpeciesCode == "WhiteSpruce" ~ "PIGL",
    SpeciesCode == "WesternWhitePine" ~ "PIMO3",
    SpeciesCode == "MountainHemlock" ~ "TSME",
    SpeciesCode == "EngelmannSpruce" ~ "PIEN",
    SpeciesCode == "AlaskaYellowCedar" ~ "CHNO",
    SpeciesCode == "RedAlder" ~ "ALRU2",
    TRUE ~ NA_character_
  ))

spp_to_use_all <- sp_table$SpeciesCodeActual
```

## Obtain species symbols and join to species codes

```{r}
#get SPCD for each species. This will be different depending on how the species are named,
#but we want a crosswalk from the names used in LANDIS to FIA SPCD somehow
#In this case, I used the USDA PLANTS symbol, which is found in the FIA species reference table
# to crosswalk to FIA species code

# sp_ref$SpeciesCode <- paste0(substr(sp_ref$GENUS, 1, 4), substr(sp_ref$SPECIES, 1, 4) %>% 
# stringr::str_to_title()) 
sp_ref$SpeciesCode <- sp_ref$SPECIES_SYMBOL

spp_crosswalk <- sp_ref[sp_ref$SPECIES_SYMBOL %in% spp_to_use_all, ] %>%
  dplyr::arrange(SPECIES_SYMBOL) %>%
  dplyr::select(SpeciesCode, SPCD)


# for seedlings, some species don't have enough to get good estimates. This table
# combines several SPCD for each species (e.g., ponderosa and washoe pine) to 
# improve parameter estimates for rare species
spp_crosswalk_combine <- tibble(SpeciesCode = spp_to_use_all,
                                SPCD = list(11, 18, 351, 375, 42, 108, 93, 94, 119, 98, 741, 746, 202, 242, 263, 264))

spp_to_use <- spp_crosswalk$SpeciesCode
spcd_to_use <- spp_crosswalk$SPCD
all_spcd <- unique(trees$SPCD)
```

## Calculate per-tree LAI contribution and plot-level LAI

```{r}
#we need to make sure the trees have ages so we can bin them
enough_trees <- table(sitetrees$SPCD) %>% `[`(which(table(sitetrees$SPCD) > 100)) %>% names()

age_model <- lm(log(AGEDIA) ~ poly(log(DIA), 3)*as.factor(SPCD), 
                data = sitetrees[!is.na(sitetrees$DIA) & !is.na(sitetrees$AGEDIA) & sitetrees$SPCD %in% enough_trees, ])
age_model2 <- lm(log(AGEDIA) ~ poly(log(DIA), 3), 
                 data = sitetrees[!is.na(sitetrees$DIA) & !is.na(sitetrees$AGEDIA), ])

trees <- trees %>%
  mutate(PLOT.YEAR = paste(PLT_CN, INVYR, sep=".")) %>%
  right_join(., plots_to_use, by = c("PLT_CN" = "CN")) %>%
  dplyr::mutate(DIA_cm = DIA * 2.54,
                HT_m = HT / 3.3808) %>%
  dplyr::filter(STATUSCD == 1) %>%
  dplyr::left_join(spgrp_lai)

for(i in 1:length(all_spcd)){
  
  spcd = all_spcd[i]
  sp = spp_crosswalk[match(spcd, spp_crosswalk$SPCD), "SpeciesCode"]
  
  if(spcd %in% enough_trees){
    
    trees[trees$SPCD == spcd, "TOTAGE2"] <- exp(predict(age_model,
                                                        newdata = trees[trees$SPCD == spcd, ]))
    
  } else{
    trees[trees$SPCD == spcd, "TOTAGE2"] <- exp(predict(age_model2,
                                                        newdata = trees[trees$SPCD == spcd, ]))
    
  }
}

trees$age <- ifelse(is.na(trees$TOTAGE), trees$TOTAGE2, trees$TOTAGE)
trees$age <- ifelse(trees$age > 500, 500, trees$age)
breaks <- seq(0, max(trees$age, na.rm = TRUE) + (10 - max(trees$age, na.rm = TRUE) %% 10), by = 5)
trees$age_bin <- base::cut(trees$age, breaks = breaks, labels = breaks[-1], right = TRUE)

trees_bin <- trees %>%
  group_by(PLOT.YEAR, SPCD, age_bin) %>%
  summarise(cohort_biomass = sum(CARBON_AG/0.47, na.rm = TRUE) * 0.11, #sum biomass and convert to g m-2
            KLAI = KLAI[1],
            MaximumLAI = MaximumLAI[1]) %>%
  mutate(LAI_tree = MaximumLAI * cohort_biomass/(KLAI + cohort_biomass))

#calculate leaf area index per plot
plot_leaf_area <- trees_bin %>%
  group_by(PLOT.YEAR) %>%
  #m2 per tree * trees per acre * acre per m2 = meters squared leaf area per meter squared ground
  summarise(LAI = sum(LAI_tree)) %>%
  filter(!is.na(LAI) & !is.infinite(LAI)) %>%
  filter(LAI < 20)

hist(plot_leaf_area$LAI)
```

## See where seedlings are present and which plots they could be present

```{r}
## get seedlings
seedlings <- seedlings %>%
  mutate(PLOT.YEAR = paste(PLT_CN, INVYR, sep="."),
         TPA_UNADJ = ifelse(is.na(TPA_UNADJ), 0, TPA_UNADJ)) %>%
  filter(PLOT.YEAR %in% plot_leaf_area$PLOT.YEAR) %>%
  # filter(TOTAGE <= 5) %>% #only useful in RMRS zone, and only collected fora  subset of trees
  group_by(PLOT.YEAR) %>%
  mutate(SEEDLING_COUNT = sum(TPA_UNADJ)) %>%
  slice_head(n = 1)


# Find how many seedlings are in each plot
# And find which plots are in the species range to use for future calculations
for (i in 1:nrow(spp_crosswalk)){print(i)
  range_method <- ifelse(is.na(range_method), "none", range_method)
  
  SPCD <- spp_crosswalk_combine[[i, "SPCD"]][[1]]
  
  seedling_sub <- seedlings[seedlings$SPCD %in% SPCD,]
  
  plot_sf <- plot  %>%
    sf::st_as_sf(coords = c("LON", "LAT")) %>%
    st_as_sf %>%
    sf::st_set_crs("EPSG:4326") %>%
    sf::st_transform("EPSG:5070") %>%
    mutate(PLOT.YEAR = paste(CN, INVYR, sep="."))
  
  if(range_method == "seedling"){
    
    seedling_sf <- left_join(seedling_sub, select(plot, CN, LAT, LON), by = c("PLT_CN" = "CN")) %>%
      sf::st_as_sf(coords = c("LON", "LAT"))%>%
      sf::st_set_crs("EPSG:4326") %>%
      sf::st_transform("EPSG:5070")
    
    #create a zone within buffer distance of seedlings
    seedling_buffer <- sf::st_buffer(seedling_sf, range_buffer) %>% 
      st_union() %>% 
      st_as_sf()
    plot_sf$in_range <- lengths(st_within(plot_sf, seedling_buffer))
    
  }else if(range_method == "adult"){
    plots_with_adults <- trees %>%
      filter(SPCD %in% SPCD) %>%
      filter(age > 20) %>% #pick an age at maturity to serve as a seed source
      `[`("PLT_CN") %>%
      unique()
    
    plot_adults <- plot[plot$CN %in% plots_with_adults$PLT_CN, ]  %>%
      sf::st_as_sf(coords = c("LON", "LAT")) %>%
      distinct(geometry) %>%
      st_as_sf %>%
      sf::st_set_crs("EPSG:4326") %>%
      sf::st_transform("EPSG:5070")
    
    plot_buffer <- sf::st_buffer(plot_adults, range_buffer) %>% 
      st_union() %>% 
      st_as_sf()
    plot_sf$in_range <- lengths(st_within(plot_sf, plot_buffer))
    
  }else{
    plot_sf$in_range <- 1
  }
  
  Table <- seedlings[seedlings$SPCD %in% SPCD,]
  
  if(nrow(Table) == 0) next #this can break the rest of the code, because further down expects a column for every species
  
  Sums <- aggregate(Table$TREECOUNT, by=list(PLOT.YEAR = Table$PLOT.YEAR), FUN=sum)
  Sums$x <- ifelse(is.na(Sums$x), 0, Sums$x)
  colnames(Sums) <- c("PLOT.YEAR", spp_to_use[i])
  
  #plots without seedlings get a 0, plots out of range get an NA
  plot_leaf_area <- left_join(plot_leaf_area, Sums, by = "PLOT.YEAR") %>%
    mutate(across(spp_to_use[i], ~ ifelse(is.na(.), 0, .))) %>%
    mutate(across(spp_to_use[i], ~ ifelse(PLOT.YEAR %in% filter(plot_sf, in_range == 1)$PLOT.YEAR,
                                          .,
                                          NA)))
  
  
}


spp_to_use2 <- spp_to_use[which(spp_to_use %in% names(plot_leaf_area))]

n_seedlings <- plot_leaf_area %>%
  tidyr::pivot_longer(cols = all_of(spp_to_use2),
                      names_to = "Species",
                      values_to = "Count") %>%
  group_by(Species) %>%
  summarize(total = sum(Count, na.rm = TRUE))

write.csv(plot_leaf_area, "data/Southeast_seedlings_with_leaf_area.csv")
```

## Finding proportion of each LAI bin with seedlings present

```{r}
#make histogram for proportion
nBins <- 30
minLAI <- 0.05
plot_seedling_histogram <- plot_leaf_area %>%
  tidyr::pivot_longer(cols = all_of(spp_to_use2),
                      names_to = "Species",
                      values_to = "Count") %>%
  mutate(LAI = ifelse(LAI < minLAI, minLAI, LAI)) %>%
  mutate(lai_bin = base::cut(LAI, breaks = nBins),
         present = ifelse(Count>0, 1, 0)) %>%
  group_by(Species, lai_bin) %>%
  summarise(n_present = sum(present, na.rm = TRUE),
            n_plots_bin = sum(!is.na(present)),
            prop_present = n_present / n_plots_bin) %>%
  ungroup() %>%
  group_by(Species) %>%
  mutate(prop_present = ifelse(is.na(prop_present), 0, prop_present)) %>%
  mutate(lai = strsplit(as.character(lai_bin), split = ",") %>% #calculate the midpoint of the bin
           map(., .f = ~gsub("\\(|\\]", "", .)) %>%
           map(., .f = ~mean(as.numeric(.))) %>%
           unlist() %>%
           as.numeric())
if(set_auc_to_1) plot_seedling_histogram <- plot_seedling_histogram %>%
  mutate(prop_present = prop_present / sum(prop_present, na.rm = TRUE)) #proportion of plots in the bin with seedlings
if(scale_max_p) plot_seedling_histogram <- plot_seedling_histogram %>%
  mutate(prop_present = prop_present * (1/max(prop_present, na.rm = TRUE))) #set the maximum prop_present to 1 
#and scale everything to match

ggplot(plot_seedling_histogram, aes(x = lai, y = prop_present, color = Species)) +
  geom_line() +
  xlab(label = "Leaf Area Index") +
  ylab(label = "Proportion of plots with seedlings")


#set bounds to parameter estimates to send to the function that fits weibull parameters.
#bound the location parameter at 0 so that we don't get negative P_est.
#You could set other constraints if you're not getting realistic shapes
species_bounds <- tibble(Species = spp_to_use)
species_bounds$lower = list(c(-Inf, -Inf, 0, 0)) #lower and upper bounds for the shape, scale, location, and adjustment parameters
species_bounds$upper = list(c(Inf, Inf, Inf, 20))

#Only if needed: for some species, set the maximum shape parameter 
# to 1 to force a negative-exponential shape
species_bounds[species_bounds$Species %in% c("PIST"), ]$upper <- list(c(1, Inf, Inf, 20))

plot_seedling_histogram <- left_join(plot_seedling_histogram, species_bounds)

#fit the models using function above, and pull out the shape and scale  
#parameters with broom::tidy()
weibull_models <- plot_seedling_histogram %>%
  mutate(PLOT.LAI = ifelse(lai < 0.1, 0.1, lai)) %>%
  ungroup() %>%
  group_by(Species) %>%
  ungroup() %>%
  dplyr::nest_by(Species) %>%
  mutate(model = list(fit_weibull(data, data$lower[[1]], data$upper[[1]], use_c_d = use_c_d))) %>%
  mutate(shape = broom::tidy(model) %>% pluck(., 2, 1),
         scale = broom::tidy(model) %>% pluck(., 2, 2),
         location = ifelse(use_c_d == "d", 0, broom::tidy(model) %>% pluck(., 2, 3, .default = 0)), #sometimes c doesn't exist; set it to 0 in that case
         adjust = broom::tidy(model) %>% pluck(., 2, ifelse(use_c_d == "d", 3, 4), .default = 1)) #sometimes d doesn't exist; set it to 0 in that case

# weibull_models_max_1 <- weibull_models
```

#Weibull plot against empirical

```{r}
#make a figure for each species with empirical data and distribution
#this is pretty gross looking but not that complicated really.
#We loop through each item of the list (.l), which loops us through each species,
#where we make a ggplot figure for each species
#newdat <- list(lai = seq(0, 20, length.out = 100))

plot_df <- pmap_dfr(
  .l = list(dat = weibull_models$data, 
            sp = weibull_models$Species,
            mod = weibull_models$model),
  .f = function(dat, sp, mod) {
    newdat <- data.frame(lai = seq(min(dat$lai), max(dat$lai), length.out = 100))
    pred <- predict(mod, newdata = newdat)

    bind_rows(
      dat %>% mutate(Source = "Observed", Species = sp),
      data.frame(lai = newdat$lai, prop_present = pred, Source = "Predicted", Species = sp)
    )
  }
)
ggplot(plot_df, aes(x = lai, y = prop_present)) +
  geom_point(data = filter(plot_df, Source == "Observed"), size = 2) +
  geom_line(data = filter(plot_df, Source == "Predicted"), color = "blue") +
  facet_wrap(~Species, scales = "free_y") +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "LAI", y = "Proportion Present")

write.csv(weibull_models[c(1,4:7)], "weibull_establishment_params.csv")
```

